---
title: "136_Liz_Project_Step4_Regressions"
author: "Hyunkyung Kim"
date: "November 6, 2018"
output:
  word_document: default
  html_document: default
---


```{r}
#install.packages("glmnet")
#install.packages("mlbench")
#install.packages("Boruta")
library(caret)
library(tidyverse)
library(psych)
library(glmnet)
library(mlbench)
library(Boruta)
library(MASS) # stepwise regression
library(leaps) # all subsets regression
library(randomForest)
```

```{r}
set.seed(999)
Mycontrols<-trainControl(method='repeatedcv',number=10, repeats=5,verboseIter = F)
```
### Import Cleaned Data

```{r}

H_Clean<-read.csv( file = "C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\H_clean.csv")

Train<-H_Clean[!is.na(H_Clean$SalePrice),-1] #Remove ID
Test<-H_Clean[is.na(H_Clean$SalePrice),-1] 
```


7 tentative attributes left: Alley, BsmtFinType2, Functional, LandSlope, MasVnrType and 2 more;
SalePrice ~ MSSubClass + MSZoning + LotFrontage + LotArea + LotShape + 
    LandContour + Neighborhood + BldgType + HouseStyle + OverallQual + 
    OverallCond + YearBuilt + YearRemodAdd + Exterior1st + Exterior2nd + 
    MasVnrArea + ExterQual + Foundation + BsmtQual + BsmtCond + 
    BsmtExposure + BsmtFinType1 + BsmtFinSF1 + BsmtUnfSF + TotalBsmtSF + 
    HeatingQC + CentralAir + X1stFlrSF + X2ndFlrSF + GrLivArea + 
    BsmtFullBath + FullBath + HalfBath + BedroomAbvGr + KitchenAbvGr + 
    KitchenQual + TotRmsAbvGrd + Fireplaces + FireplaceQu + GarageType + 
    GarageYrBlt + GarageFinish + GarageCars + GarageArea + GarageQual + 
    GarageCond + PavedDrive + WoodDeckSF + OpenPorchSF+
    Alley+RoofStyle+BsmtFinType2+SaleCondition

Selected Feature from Boruta - random forest selection

 [1] "MSSubClass"    "MSZoning"      "LotFrontage"   "LotArea"       "Alley"         "LotShape"      "LandContour"   "LandSlope"    
 [9] "Neighborhood"  "BldgType"      "HouseStyle"    "OverallQual"   "OverallCond"   "YearBuilt"     "YearRemodAdd"  "RoofStyle"    
[17] "Exterior1st"   "Exterior2nd"   "MasVnrArea"    "ExterQual"     "Foundation"    "BsmtQual"      "BsmtCond"      "BsmtExposure" 
[25] "BsmtFinType1"  "BsmtFinSF1"    "BsmtFinType2"  "BsmtUnfSF"     "TotalBsmtSF"   "HeatingQC"     "CentralAir"    "X1stFlrSF"    
[33] "X2ndFlrSF"     "GrLivArea"     "BsmtFullBath"  "FullBath"      "HalfBath"      "BedroomAbvGr"  "KitchenAbvGr"  "KitchenQual"  
[41] "TotRmsAbvGrd"  "Fireplaces"    "FireplaceQu"   "GarageType"    "GarageYrBlt"   "GarageFinish"  "GarageCars"    "GarageArea"   
[49] "GarageQual"    "GarageCond"    "PavedDrive"    "WoodDeckSF"    "OpenPorchSF"   "SaleCondition"

```{r}

```
#### Forward Selection results- Option 2.

lm(formula = SalePrice ~ OverallQual + GrLivArea + Neighborhood + 
    BsmtFinSF1 + RoofMatl + MSSubClass + BsmtExposure + KitchenQual + 
    Condition2 + SaleCondition + LotArea + YearBuilt + OverallCond + 
    MasVnrArea + PoolQC + BedroomAbvGr + GarageCars + GarageFinish + 
    TotalBsmtSF + BldgType + MasVnrType + Functional + ExterQual + 
    BsmtCond + Condition1 + Exterior1st + LandContour + MoSold + 
    ScreenPorch + LowQualFinSF + LotConfig + LotFrontage + WoodDeckSF + 
    Street + GarageArea + KitchenAbvGr + TotRmsAbvGrd + LotShape + 
    ExterCond + PoolArea + BsmtFinSF2 + Fireplaces + FireplaceQu + 
    BsmtQual + X3SsnPorch + Foundation + Utilities, data = Train)



```{r}

```
### Backwards Elimination results - Option 3.


lm(formula = SalePrice ~ LotFrontage + LotArea + Street + LandContour + 
    LotConfig + Neighborhood + Condition1 + Condition2 + BldgType + 
    HouseStyle + OverallQual + OverallCond + YearBuilt + RoofMatl + 
    Exterior1st + MasVnrType + MasVnrArea + ExterQual + ExterCond + 
    Foundation + BsmtQual + BsmtCond + BsmtExposure + BsmtFinSF1 + 
    BsmtFinSF2 + BsmtUnfSF + X1stFlrSF + X2ndFlrSF + BedroomAbvGr + 
    KitchenAbvGr + KitchenQual + TotRmsAbvGrd + Functional + 
    Fireplaces + FireplaceQu + GarageFinish + GarageCars + GarageArea + 
    GarageQual + GarageCond + WoodDeckSF + X3SsnPorch + ScreenPorch + 
    PoolQC + Fence + MiscFeature + MoSold + SaleCondition, data = Train)
    
    
```{r}
par(mfrow=c(2,4))
for (i in 1:79)
(
plot(Train[,i],Train$SalePrice, las=2,  xlab=colnames(Train[i]))
)
```
set.seed(999)
```{r}
set.seed(9999)
Mycontrols<-trainControl(method='repeatedcv',number=10, repeats=5,verboseIter = T)
```


```{r}
#MyIndex<-sample(2,nrow(Train),replace=T,prob=c(0.7,0.3))
```
#### Linear Regression

```{r}
myLm1<-lm(SalePrice~.,data=Train)
myLm2<-lm(SalePrice ~ OverallQual + GrLivArea + Neighborhood + 
    BsmtFinSF1 + RoofMatl + MSSubClass + BsmtExposure + KitchenQual + 
    Condition2 + SaleCondition + LotArea + YearBuilt + OverallCond + 
    MasVnrArea + PoolQC + BedroomAbvGr + GarageCars + GarageFinish + 
    TotalBsmtSF + BldgType + MasVnrType + Functional + ExterQual + 
    BsmtCond + Condition1 + Exterior1st + LandContour + MoSold + 
    ScreenPorch + LowQualFinSF + LotConfig + LotFrontage + WoodDeckSF + 
    Street + GarageArea + KitchenAbvGr + TotRmsAbvGrd + LotShape + 
    ExterCond + PoolArea + BsmtFinSF2 + Fireplaces + FireplaceQu + 
    BsmtQual + X3SsnPorch + Foundation + Utilities, data = Train)
myLm3<-lm(formula = SalePrice ~ LotFrontage + LotArea + Street + LandContour + 
    LotConfig + Neighborhood + Condition1 + Condition2 + BldgType + 
    HouseStyle + OverallQual + OverallCond + YearBuilt + RoofMatl + 
    Exterior1st + MasVnrType + MasVnrArea + ExterQual + ExterCond + 
    Foundation + BsmtQual + BsmtCond + BsmtExposure + BsmtFinSF1 + 
    BsmtFinSF2 + BsmtUnfSF + X1stFlrSF + X2ndFlrSF + BedroomAbvGr + 
    KitchenAbvGr + KitchenQual + TotRmsAbvGrd + Functional + 
    Fireplaces + FireplaceQu + GarageFinish + GarageCars + GarageArea + 
    GarageQual + GarageCond + WoodDeckSF + X3SsnPorch + ScreenPorch + 
    PoolQC + Fence + MiscFeature + MoSold + SaleCondition, data = Train)
    

summary(myLm1)
summary(myLm2)
summary(myLm3)
```



myLm<-train(
  SalePrice ~., data = Train,
  method='lm', trControl=Mycontrols)



#Lasso

```{r}
myLasso<-train(
  SalePrice ~ OverallQual + GrLivArea + Neighborhood + 
    BsmtFinSF1 + RoofMatl + MSSubClass + BsmtExposure + KitchenQual + 
    Condition2 + SaleCondition + LotArea + YearBuilt + OverallCond + 
    MasVnrArea + PoolQC + BedroomAbvGr + GarageCars + GarageFinish + 
    TotalBsmtSF + BldgType + MasVnrType + Functional + ExterQual + 
    BsmtCond + Condition1 + Exterior1st + LandContour + MoSold + 
    ScreenPorch + LowQualFinSF + LotConfig + LotFrontage + WoodDeckSF + 
    Street + GarageArea + KitchenAbvGr + TotRmsAbvGrd + LotShape + 
    ExterCond + PoolArea + BsmtFinSF2 + Fireplaces + FireplaceQu + 
    BsmtQual + X3SsnPorch + Foundation + Utilities, data = Train
  ,method='glmnet',tuneGrid=expand.grid(alpha=1,lambda=seq(0.0001,2000,length=10)), trControl=Mycontrols)

```


```{r}
plot(myLasso)
plot(varImp(myLasso), Scale=F)
varImp(myLasso)
myLasso$bestTune
myLasso
plot(myLasso$finalModel)
coef(myLasso)
```

```{r}
myEla<-train(SalePrice~.,Train,method='glmnet',tuneGrid=expand.grid(alpha=seq(0, 1,length=10),lambda=seq(0.0001,2000,length=20)), trControl=Mycontrols)
```
```{r}
plot(myEla)
plot(varImp(myEla))
varImp(myEla)
myEla$bestTune
myEla
```