---
title: "Untitled"
author: "Hyunkyung Kim"
date: "November 3, 2018"
output: html_document
---

```{r, echo=FALSE}
#install.packages("glmnet")
#install.packages("mlbench")
library(caret)
library(plyr)
library(tidyverse)
library(psych)
library(glmnet)
library(mlbench)
library(mice)

```


### Step 1 was used with test data only, but this step includes cleaning up of test set and train set.

##### Read train and test dataset and combine

```{r}

H_train<-read.csv("C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\train.csv")
H_test<-read.csv("C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\test.csv")

H_Orig<-rbind.fill(H_train,H_test) #rbind.fill does fill with NA values if column is missing. in here Saleprice missing for test data.
H_Working<-H_Orig # Save a copy

tail(H_Orig)
```


#### Check for duplicates

```{r}

nrow(H_Working[,-1])
nrow(unique(H_Working[,-c(1,81)]))



```
* We have 2 pairs of duplicates. Both are exact same except one is in the training, one is in the test set. Will leave as is for now.
* ID 194/2866 and 830/2714 appears to be the same.


### DATA CLEANING & Working with N/As

#### CHeck for N/As
```{r}
NAs<-colSums(is.na(H_Working))

# Percentage
NAs[NAs>0]
round(NAs[NAs>0]/nrow(H_Working)*100,digits=2)
```

#### Below are the items to change from factors to numerics

Col Name	type	N/A(%)	R - Output	Description
FireplaceQu	F	47%	Factor w/ 5 levels "Ex","Fa","Gd",..: NA 5 5 3 5 NA 3 5 5 5 ...	 Fireplace quality
ExterCond	F	0%	Factor w/ 5 levels "Ex","Fa","Gd",..: 5 5 5 5 5 5 5 5 5 5 ...	 Evaluates the present condition of the material on the exterior
GarageCond	F	6%	Factor w/ 5 levels "Ex","Fa","Gd",..: 5 5 5 5 5 5 5 5 5 5 ...	 Garage condition
GarageQual	F	6%	Factor w/ 5 levels "Ex","Fa","Gd",..: 5 5 5 5 5 5 5 5 2 3 ...	 Garage quality
HeatingQC	F	0%	Factor w/ 5 levels "Ex","Fa","Gd",..: 1 1 1 3 1 1 1 1 3 1 ...	 Heating quality and condition
ExterQual	F	0%	Factor w/ 4 levels "Ex","Fa","Gd",..: 3 4 3 4 3 4 3 4 4 4 ...	 Evaluates the quality of the material on the exterior 
KitchenQual	F	0%	Factor w/ 4 levels "Ex","Fa","Gd",..: 3 4 3 3 3 4 3 4 4 4 ...	 Kitchen quality
BsmtQual	F	3%	Factor w/ 4 levels "Ex","Fa","Gd",..: 3 3 3 4 3 3 1 3 4 4 ...	 Evaluates the height of the basement
PoolQC	F	100%	Factor w/ 3 levels "Ex","Fa","Gd": NA NA NA NA NA NA NA NA NA NA ...	 Pool quality
BsmtCond     : Factor w/ 4 levels "Fa","Gd","Po",..: 4 4 4 2 4 4 4 4 4 4 ...

Functional	F	0%	Factor w/ 7 levels "Maj1","Maj2",..: 7 7 7 7 7 7 7 7 3 7 ...
BsmtFinType2	F	3%	Factor w/ 6 levels "ALQ","BLQ","GLQ",..: 6 6 6 6 6 6 6 2 6 6 ...
BsmtFinType1	F	3%	Factor w/ 6 levels "ALQ","BLQ","GLQ",..: 3 1 3 1 3 3 3 1 6 3 ...
Fence	F	81%	Factor w/ 4 levels "GdPrv","GdWo",..: NA NA NA NA NA 3 NA NA NA NA ...
BsmtExposure	F	3%	Factor w/ 4 levels "Av","Gd","Mn",..: 4 2 3 4 1 4 1 3 4 4 ...
PavedDrive	F	0%	Factor w/ 3 levels "N","P","Y": 3 3 3 3 3 3 3 3 3 3 ...
LandSlope	F	0%	Factor w/ 3 levels "Gtl","Mod","Sev": 1 1 1 1 1 1 1 1 1 1 ...
GarageFinish	F	6%	Factor w/ 3 levels "Fin","RFn","Unf": 2 2 2 3 2 3 2 2 3 2 ...

### For factors including Ex, Fa, Gd, Po, TA ones:
Function created to automate some of ordinals to numerics and check before and after the transformation.

```{r}

Exorder<-function(x){ # Reorder Ex,Fa,Gd,Po,TA order ones into 1,2,3,4,5 and check before and after. Retiring this since it somehow doesn't work.
H_Working[,x]<-as.numeric(recode(H_Orig[,x],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
print(table(H_Orig[,x],useNA = 'ifany'))
print(table(H_Working[,x],useNA ='ifany'))
}


# BnF - This is to compare before and after transformation. Need quotation before and after.
BnF<-function(x){
  
print(table(H_Orig[,x],useNA = 'ifany'))
print(table(H_Working[,x],useNA ='ifany'))

}

```

FireplaceQu	F	47%	Factor w/ 5 levels "Ex","Fa","Gd",..: NA 5 5 3 5 NA 3 5 5 5 ...	 Fireplace quality
ExterCond	F	0%	Factor w/ 5 levels "Ex","Fa","Gd",..: 5 5 5 5 5 5 5 5 5 5 ...	 Evaluates the present condition of the material on the exterior
GarageCond	F	6%	Factor w/ 5 levels "Ex","Fa","Gd",..: 5 5 5 5 5 5 5 5 5 5 ...	 Garage condition
GarageQual	F	6%	Factor w/ 5 levels "Ex","Fa","Gd",..: 5 5 5 5 5 5 5 5 2 3 ...	 Garage quality
HeatingQC	F	0%	Factor w/ 5 levels "Ex","Fa","Gd",..: 1 1 1 3 1 1 1 1 3 1 ...	 Heating quality and condition
ExterQual	F	0%	Factor w/ 4 levels "Ex","Fa","Gd",..: 3 4 3 4 3 4 3 4 4 4 ...	 Evaluates the quality of the material on the exterior 
KitchenQual	F	0%	Factor w/ 4 levels "Ex","Fa","Gd",..: 3 4 3 3 3 4 3 4 4 4 ...	 Kitchen quality
BsmtQual	F	3%	Factor w/ 4 levels "Ex","Fa","Gd",..: 3 3 3 4 3 3 1 3 4 4 ...	 Evaluates the height of the basement
PoolQC	F	100%	Factor w/ 3 levels "Ex","Fa","Gd": NA NA NA NA NA NA NA NA NA NA ...	 Pool quality


```{r}
H_Working[,"FireplaceQu"]<-as.numeric(recode(H_Orig[,"FireplaceQu"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
# Imputing 1460NA - matches with 0 fireplaces.
H_Working$FireplaceQu[is.na(H_Orig$FireplaceQu)]<-0
BnF('FireplaceQu')

# no NA
H_Working[,"ExterCond"]<-as.numeric(recode(H_Orig[,"ExterCond"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
BnF('ExterCond')

# Garage Items will look together
H_Working[,"GarageCond"]<-as.numeric(recode(H_Orig[,"GarageCond"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
BnF('GarageCond')
H_Working[,"GarageQual"]<-as.numeric(recode(H_Orig[,"GarageQual"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
BnF('GarageQual')

# no NA
H_Working[,"HeatingQC"]<-as.numeric(recode(H_Orig[,"HeatingQC"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
BnF('HeatingQC')

# no NA
H_Working[,"ExterQual"]<-as.numeric(recode(H_Orig[,"ExterQual"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
BnF('ExterQual')

# Replacing NA with TA (most common item - Kitchen exists for this row)
H_Working[,"KitchenQual"]<-as.numeric(recode(H_Orig[,"KitchenQual"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
H_Working$KitchenQual[is.na(H_Orig$KitchenQual)]<-0
BnF('KitchenQual')


# 3 rows NA - PoolArea >0 but NA on pool condition. Will impute good=4 (Good and Ex ties).
# Rest of NAs will be 0
H_Working[,"PoolQC"]<-as.numeric(recode(H_Orig[,"PoolQC"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
H_Working$PoolQC[is.na(H_Orig$PoolQC) & H_Orig$PoolArea>0]<-4
H_Working$PoolQC[is.na(H_Working$PoolQC)]<-0
BnF('PoolQC')

# Will work with Bmst Nas together
H_Working[,"BsmtCond"]<-as.numeric(recode(H_Orig[,"BsmtCond"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
BnF('BsmtCond')
H_Working[,"BsmtQual"]<-as.numeric(recode(H_Orig[,"BsmtQual"],Ex=5,Fa=2,Gd=4,Po=1,TA=3))
BnF('BsmtQual')

#Exorder('FireplaceQu')
#Exorder('ExterCond')
#Exorder('GarageCond')
#Exorder('GarageQual')
#Exorder('HeatingQC')
#Exorder('ExterQual')
#Exorder('KitchenQual')
#Exorder('BsmtQual')
#Exorder('PoolQC')
#Exorder('BsmtCond')
```
They look good. 


* Functional	F	0%	Factor w/ 7 levels "Maj1","Maj2",..: 7 7 7 7 7 7 7 7 3 7 ...
Also Impute 2 missing value with most common value (over 90%)

7       Typ	Typical Functionality
6       Min1	Minor Deductions 1
5       Min2	Minor Deductions 2
4       Mod	Moderate Deductions
3       Maj1	Major Deductions 1
2       Maj2	Major Deductions 2
1        Sev	Severely Damaged
0       Sal	Salvage only


```{r}
levels(H_Orig$Functional)
```

So order should be 3, 2, 6, 5, 4, 1, 7
```{r}
H_Working$Functional<-c(3,2,6,5,4,1,7)[as.numeric(H_Orig$Functional)]

# Majority are Typ so will impute to that for 2 NAs
H_Working$Functional[is.na(H_Orig$Functional)]<-7

table(H_Orig$Functional,useNA = 'ifany')
table(H_Working$Functional,useNA = 'ifany')

```

* Other Basment Related ordinal variables
BsmtFinType1: BsmtFinType1: Rating of basement finished area
BsmtFinType2: Rating of basement finished area (if multiple types)	
	
6       GLQ	Good Living Quarters
5       ALQ	Average Living Quarters
4       BLQ	Below Average Living Quarters
3       Rec	Average Rec Room
2       LwQ	Low Quality
1       Unf	Unfinshed
0       NA	No Basement


```{r}
levels(H_Orig$BsmtFinType2)
levels(H_Orig$BsmtFinType1)
```

Order should be 5,4,6,2,3,1

```{r}
H_Working$BsmtFinType1<-c(5,4,6,2,3,1)[as.numeric(H_Orig$BsmtFinType1)]

H_Working$BsmtFinType2<-c(5,4,6,2,3,1)[as.numeric(H_Orig$BsmtFinType2)]

BnF('BsmtFinType1')
#table(H_Orig$BsmtFinType1,useNA ='ifany')
#table(H_Working$BsmtFinType1,useNA ='ifany')
BnF('BsmtFinType2')
#table(H_Orig$BsmtFinType2,useNA ='ifany')
#table(H_Working$BsmtFinType2, useNA = 'ifany')


```

* BsmtExposure: Refers to walkout or garden level walls	
	
4       Gd	Good Exposure
3       Av	Average Exposure (split levels or foyers typically score average or above)
2       Mn	Mimimum Exposure
1       No	No Exposure
0       NA	No Basement


```{r}
levels(H_Orig$BsmtExposure)
```
Again, looking at data itself, I can see that one row is a mistake in putting in NA instead of No.  

To fix this I'm going to use two conditions. All BsmtFinType1 Unf and BsmtExposure NA to 1 (No) then I will move rest to 0 (NA).
3 houses associated.


```{r}
H_Working$BsmtExposure<-c(3,4,2,1)[as.numeric(H_Orig$BsmtExposure)]
H_Working$BsmtExposure[is.na(H_Orig$BsmtExposure) & H_Orig$BsmtFinType1=='Unf']<-1
H_Working$BsmtExposure[is.na(H_Working$BsmtExposure)]<-0

table(H_Orig$BsmtExposure,useNA='ifany')
table(H_Working$BsmtExposure,useNA='ifany')
```
* Look at other values in Bsmt 
ALL related items are transformed into numerical values for Bsmt. Now impute rest of the missing values regarding basement.
It looks like 79 itmes are related to actually not having basements. Rest are mistakes.

BsmtQual	81 -  79NA to 0 , 2 use most common item
BsmtCond	82 -  79NA to 0 , 2 use most common item
+ BsmtExposure	82 - 79NA to 0, 3 to No=0 (no exposure - applied above )
+ BsmtFinType1	79 - 79NA to 0
+ BsmtFinSF1	1 - to 0 (typo - no basement)
+ BsmtFinType2	80 -79NA one to most common item
+ BsmtFinSF2	1 - to 0 (typo - no basement)
+ BsmtUnfSF	1 - to 0 (typo - no basement)
+ TotalBsmtSF	1 - to 0 (typo - no basement)
BsmtFullBath	2
BsmtHalfBath	2

Among this, 


BsmtQual	BsmtCond	BsmtExposure	BsmtFinType1	BsmtFinSF1	BsmtFinType2	BsmtFinSF2	BsmtUnfSF	TotalBsmtSF
NA	NA	NA	NA	NA	NA	NA	NA	NA

This row is responsible for - they should all be 0

BsmtFinSF1	1  
BsmtFinSF2	1
BsmtUnfSF	1
TotalBsmtSF	1

```{r}
H_Working$BsmtFinSF1[is.na(H_Orig$BsmtFinSF1)]<-0
H_Working$BsmtFinSF2[is.na(H_Orig$BsmtFinSF2)]<-0
H_Working$BsmtUnfSF[is.na(H_Orig$BsmtUnfSF)]<-0
H_Working$TotalBsmtSF[is.na(H_Orig$TotalBsmtSF)]<-0

# Check Before and After for Each - coutn of 0 should increase by one.
sum((H_Orig$BsmtFinSF1==0),na.rm=T)
sum((H_Working$BsmtFinSF1==0))
sum((H_Orig$BsmtFinSF2==0),na.rm=T)
sum((H_Working$BsmtFinSF2==0))
sum((H_Orig$BsmtUnfSF==0),na.rm=T)
sum((H_Working$BsmtUnfSF==0))
sum((H_Orig$TotalBsmtSF==0),na.rm=T)
sum((H_Working$TotalBsmtSF==0))


```                      
                          
                          

# Here, this NA for H_Working$BsmtFinType2 is a typo for 1 row. Looking at the data itself, 479Sf of Basement 2 exists.
# For this row, I will impute the value to the most frequent item when the Basement 2 exist which is Rec from the table.

ALQ  BLQ  GLQ  LwQ  Rec  Unf <NA> 
  19   33   14   46   54 1256   38 

This row had unique 479 square foot for BsmtFinSF2, so I will use this condition to impute that first. So that row will have 3(Rec) for its value. Rest will have value 0 for having no basement

```{r}
H_Working$BsmtFinType2[H_Working$BsmtFinSF2==479]<-3
H_Working$BsmtFinType2[is.na(H_Working$BsmtFinType2)]<-0

# Also fill in 79 NA for Type1
H_Working$BsmtFinType1[is.na(H_Working$BsmtFinType1)]<-0

table(H_Orig$BsmtFinType2,useNA ='ifany')
table(H_Working$BsmtFinType2, useNA = 'ifany')

table(H_Orig$BsmtFinType1,useNA ='ifany')
table(H_Working$BsmtFinType1,useNA ='ifany')

```


Can see one increased from 105(Rec) to 106(3) and NA decreased from 80(NA) to 79(0) for BsmtFinType2, and BsmtFinType1 NA replaced by 0.


+ BsmtQual	81 -  79NA to 0 , 2 use most common item - TA (3)
+ BsmtCond	82 -  79NA to 0 , 3 use most common item - TA (3)

```{r}
H_Working$BsmtQual[is.na(H_Orig$BsmtQual) & !is.na(H_Orig$BsmtCond)]<-3
H_Working$BsmtQual[is.na(H_Working$BsmtQual)]<-0
BnF('BsmtQual')

H_Working$BsmtCond[is.na(H_Orig$BsmtCond) & !is.na(H_Orig$BsmtQual)]<-3
H_Working$BsmtCond[is.na(H_Working$BsmtCond)]<-0
BnF('BsmtCond')

```

+ Basement Bathrooms
They are from no basement house data, so will impute 0 for both.
```{r}
H_Working$BsmtFullBath[is.na(H_Working$BsmtFullBath)]<-0
H_Working$BsmtHalfBath[is.na(H_Working$BsmtHalfBath)]<-0

BnF('BsmtFullBath')
BnF('BsmtHalfBath')

```




# PavedDrive: Paved driveway	
	
2       Y	Paved 
1       P	Partial Pavement
0       N	Dirt/Gravel

```{r}
levels(H_Orig$PavedDrive)
```
```{r}
H_Working$PavedDrive<-c(0,1,2)[as.numeric(H_Orig$PavedDrive)]

table(H_Orig$PavedDrive, useNA='ifany')
table(H_Working$PavedDrive, useNA='ifany')
```

#LandSlope: Slope of property	
	
3      Gtl	Gentle slope
2       Mod	Moderate Slope
1       Sev	Severe Slope

```{r}
levels(H_Orig$LandSlope)
```

```{r}
H_Working$LandSlope<-c(3,2,1)[as.factor(H_Orig$LandSlope)]
table(H_Orig$LandSlope, useNA='ifany')
table(H_Working$LandSlope, useNA = 'ifany')
```

##### Utilities: Type of utilities available, and impute 2 NA to common value
	
4      AllPub	All public Utilities (E,G,W,& S)
3     NoSewr	Electricity, Gas, and Water (Septic Tank)
2     NoSeWa	Electricity and Gas Only
1     ELO	Electricity only


```{r}
levels(H_Orig$Utilities)
```

```{r}
H_Working$Utilities<-c(4,1)[as.numeric(H_Orig$Utilities)]
#impute common value -4
H_Working$Utilities[is.na(H_Orig$Utilities)]<-4
table(H_Orig$Utilities,useNA = 'ifany')
table(H_Working$Utilities,useNA ='ifany')
```

Two levels - didn't really need to be changed to ordinal since the rest didn't exist


# BldgType: Type of dwelling	
	
  5    1Fam	Single-family Detached
  4     2FmCon	Two-family Conversion; originally built as one-family dwelling
  3     Duplx	Duplex
  2     TwnhsE	Townhouse End Unit
  1     TwnhsI	Townhouse Inside Unit
```{r}
levels(H_Orig$BldgType)
```

```{r}
H_Working$BldgType<-c(5,4,3,1,2)[H_Orig$BldgType]
table(H_Orig$BldgType, useNA = 'ifany')
table(H_Working$BldgType,useNA = 'ifany')
```
Not sure if I should combine duplex and 2fmCon

###### GarageFinish: Interior finish of the garage	
	
3       Fin	Finished
2       RFn	Rough Finished
1       Unf	Unfinished
0       NA	No Garage

# Will Impute 159 NA into 0 too
```{r}
H_Working$GarageFinish<-c(3,2,1)[as.numeric(H_Orig$GarageFinish)]
H_Working$GarageFinish[is.na(H_Working$GarageFinish)]<-0
table(H_Orig$GarageFinish,useNA='ifany')
table(H_Working$GarageFinish,useNA = 'ifany')
```


#### Ordinal changes from factors to numerics are complete. Now do the rest of NA imputation.

Below are N/As because they do not have Garage. Each has mostly 157 to 159 NAs.

GarageType  157
GarageYrBlt 159
GarageFinish  159 
GarageCars   1
GarageArea 1
GarageQual 159
GarageCond 159

There are 3 more items that has 2 more NAs than GarageType. Look into this.

Here we have 2 extra N/As for GarageYrBlt/GarageQual/GarageFinish from GarageType           

GarageType	GarageYrBlt	GarageFinish	GarageCars	GarageArea	GarageQual	GarageCond
ROW1- Detchd	NA	NA	1	360	NA	NA
ROW2- Detchd	NA	NA	NA	NA	NA	NA

First one seems to have Garage Area and # of GarageCars so looks valid. Will impute the GarageYrBlt as BuiltYear, GarageFinish/Qual/Con most common ones
```{r}
table(H_Orig$GarageFinish, useNA = 'ifany')
table(H_Orig$GarageQual, useNA = 'ifany')
table(H_Orig$GarageCond, useNA='ifany')
```
Unf/TA/TA are the most common items.
Changes : GarageYrBlt->Builtyear, GarageFinish->Unf, GarageQual<-TA, GarageCon<-TA


```{r}
#H_Working$GarageYrBlt[is.na(H_Orig$GarageYrBlt)]<-0
H_Orig$YearBuilt[is.na(H_Orig$GarageYrBlt) & H_Orig$GarageArea==360]
H_Working$GarageYrBlt[is.na(H_Orig$GarageYrBlt) & H_Orig$GarageArea==360]<-min(H_Orig$YearBuilt[is.na(H_Orig$GarageYrBlt) & H_Orig$GarageArea==360], na.rm=T)

#CHECK
BnF('GarageYrBlt')


H_Working$GarageFinish[is.na(H_Orig$GarageYrBlt) & H_Orig$GarageArea==360]<-"Unf"
H_Working$GarageQual[is.na(H_Orig$GarageYrBlt) & H_Orig$GarageArea==360]<-"TA"
H_Working$GarageCond[is.na(H_Orig$GarageYrBlt) & H_Orig$GarageArea==360]<-"TA"

#CHeck
BnF('GarageFinish')
BnF('GarageQual')
BnF('GarageCond')

#H_Orig$GaragYrBlt
#H_Working$GarageYrBlt
```
Second one has all NAs, so this is probably a typing error of detached instead of NA. 
Changes : Detchd-> NA, GarageCars ->0, GarageArea->0 (Can change Along with other NAs, GarageQual->0 GarageCond->0 later)

```{r}
H_Working$GarageType[is.na(H_Orig$GarageArea) & H_Orig$GarageType=='Detchd']<-NA
H_Working$GarageCars[is.na(H_Orig$GarageArea) & H_Orig$GarageType=='Detchd']<-0
H_Working$GarageArea[is.na(H_Orig$GarageArea) & H_Orig$GarageType=='Detchd']<-0
BnF('GarageType')
BnF('GarageCars')
# BnF('GarageArea') # GarageArea ==0 increaed in a number. Should check in more easier way.
```
Looks like worked as expected. This increased # of GarageType NA to 158.


# GarageType: Garage location	
	
       2Types	More than one type of garage
       Attchd	Attached to home
       Basment	Basement Garage
       BuiltIn	Built-In (Garage part of house - typically has room above garage)
       CarPort	Car Port
       Detchd	Detached from home
       NA	No Garage
	
Imptue NA to NoGarage


```{r}

# Garage Type NA change to NoGarage. Using different way to add another factor into the level.
H_Working$GarageType<-as.character(H_Working$GarageType)
H_Working$GarageType[is.na(H_Working$GarageType)]<-"NoGarage"

H_Working$GarageType<-as.factor(H_Working$GarageType)

table(H_Orig$GarageType,useNA = 'ifany')
table(H_Working$GarageType,useNA ='ifany')

```



```{r}
H_Working$GarageQual[is.na(H_Working$GarageQual)]<-0
H_Working$GarageCond[is.na(H_Working$GarageCond)]<-0
BnF('GarageQual')
BnF('GarageCond')
```
Looks as intended.


##### GarageYrBlt
This is a ordinal value (year), so I have decided to give the same year as year built.
##### Also the 2207 is impossible value so impute that to also the year built.

all$GarageYrBlt[is.na(all$GarageYrBlt)] <- all$YearBuilt[is.na(all$GarageYrBlt)]

```{r}
H_Working$GarageYrBlt[is.na(H_Working$GarageYrBlt)]<-H_Orig$YearBuilt[is.na(H_Working$GarageYrBlt)]

H_Working$GarageYrBlt[H_Orig$GarageYrBlt==2207]<-H_Working$YearBuilt[which(H_Orig$GarageYrBlt==2207)]
BnF('GarageYrBlt')


```

Impute some Factors NA - Fence, Alley, MiscFeature into NoFence NoAlley NoMiscFeature

```{r}
levels(H_Working$Fence)<-c(levels(H_Working$Fence),"NoFence")
H_Working$Fence[is.na(H_Orig$Fence)]<-"NoFence"
BnF("Fence")

levels(H_Working$Alley)<-c(levels(H_Working$Alley),"NoAlley")
H_Working$Alley[is.na(H_Orig$Alley)]<-"NoAlley"
BnF("Alley")

levels(H_Working$MiscFeature)<-c(levels(H_Working$MiscFeature),"NoMiscFeature")
H_Working$MiscFeature[is.na(H_Orig$MiscFeature)]<-"NoMiscFeature"
BnF("MiscFeature")

```

#### MS zoning - Majority are RL - impute to RL
```{r}
#table(H_Orig$MSZoning) - this was to check majority
H_Working$MSZoning[is.na(H_Orig$MSZoning)]<-'RL'
BnF('MSZoning')
```

Exterior1st: Exterior covering on house	
```{r}
#table(H_Orig$Exterior1st)  #this was to check majority, VinylSd for both.
#table(H_Orig$Exterior2nd)

H_Working$Exterior1st[is.na(H_Orig$Exterior1st)]<-'VinylSd'
H_Working$Exterior2nd[is.na(H_Orig$Exterior2nd)]<-'VinylSd'
BnF('Exterior1st')
BnF('Exterior2nd')
```
VinylSd increased by 1 for both.
    


##### Left Over NAs
LotFrontage  MasVnrType  MasVnrArea  Electrical    SaleType  
        486          24          23           1           1     

One row has Area but no MasVnrType - will impute that row with majority item- BrkFace. Rest will be Type - none, Area 0

MasVnrType: Masonry veneer type	-> to None
MasVnrArea: Masonry veneer area in square feet -> to 0	
       BrkCmn	Brick Common
       BrkFace	Brick Face
       CBlock	Cinder Block
       None	None
       Stone	Stone
	

```{r}
table(H_Orig$MasVnrType)
```

```{r}
H_Working$MasVnrType[!is.na(H_Orig$MasVnrArea) & is.na(H_Orig$MasVnrType)]<-'BrkFace'
H_Working$MasVnrType[is.na(H_Working$MasVnrType)]<-"None"
H_Working$MasVnrArea[is.na(H_Working$MasVnrArea)]<-0

BnF('MasVnrType')
BnF('MasVnrArea')
```


# Electrical

This probably is a typo since this is a newly built building and other facilities are there.It has central air, and gas, all utilities so it should have something decent.

I haved decided to look at this for anything that were built after 2000 and impute the most common one from there

       SBrkr	Standard Circuit Breakers & Romex
       FuseA	Fuse Box over 60 AMP and all Romex wiring (Average)
       FuseF	60 AMP Fuse Box and mostly Romex wiring (Fair)
       FuseP	60 AMP Fuse Box and mostly knob & tube wiring (poor)
       Mix	Mixed


```{r}
table(H_Orig$Electrical[H_Orig$YearBuilt>=2000])
```
After 2000, evertyhing was Sbrkr

```{r}
H_Working$Electrical[is.na(H_Working$Electrical)]<-'SBrkr'
table(H_Orig$Electrical,useNA='ifany')
table(H_Working$Electrical,useNA='ifany')

```
##### SaleType
```{r}
#table(H_Orig$SaleType)#To find out majority'
H_Working$SaleType[is.na(H_Orig$SaleType)]<-'WD'
BnF('SaleType')
```
#### Lot Frontage Imputation

This is done using mice package.



```{r}

H_Working_1<-H_Working[,-80] # Exclude SalePrice
H_Working_2<- mice(H_Working_1, m=1, method='cart', printFlag=FALSE)
```
Imputed Value
```{r}
xyplot(H_Working_2,LotFrontage~LotArea)
```

