---
title: "136_Liz_Project_Step4_Regressions"
author: "Hyunkyung Kim"

output:
  word_document: default
  html_document: default
---


```{r}
#install.packages("glmnet")
#install.packages("mlbench")
#install.packages("Boruta")
library(caret)
library(tidyverse)
library(psych)
library(glmnet)
library(mlbench)
library(Boruta)
library(MASS) # stepwise regression
library(leaps) # all subsets regression
library(randomForest)
library(MLmetrics)
library(e1071)
```

### Import Cleaned Data

```{r}

H_Clean<-read.csv( file = "C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\H_clean.csv")

Train<-H_Clean[!is.na(H_Clean$SalePrice),-1] #Remove ID
Test<-H_Clean[is.na(H_Clean$SalePrice),-1] 
```

### For cross validataion.
```{r}
set.seed(999)
Mycontrols<-trainControl(method='repeatedcv',number=10, repeats=5,verboseIter = F)
```


#### Forward Selection results- Option 1.

Model 1: SalePrice ~ OverallQual + GrLivArea + Neighborhood + BsmtFinSF1 + 
    RoofMatl + MSSubClass + BsmtExposure + KitchenQual + Condition2 + 
    SaleCondition + LotArea + YearBuilt + OverallCond + MasVnrArea + 
    PoolQC + BedroomAbvGr + GarageCars + MasVnrType + TotalBsmtSF + 
    BldgType + Functional + ExterQual + BsmtCond + Condition1 + 
    Exterior1st + MoSold + GarageCond + ScreenPorch + LandContour + 
    LowQualFinSF + LotConfig + LotFrontage + TotRmsAbvGrd + KitchenAbvGr + 
    WoodDeckSF + Street + GarageArea + LotShape + BsmtQual + 
    Fireplaces + FireplaceQu + PoolArea + RoofStyle + BsmtFinSF2 + 
    Utilities + ExterCond

c(OverallQual , GrLivArea , Neighborhood , BsmtFinSF1 , 
    RoofMatl , MSSubClass , BsmtExposure , KitchenQual , Condition2 , 
    SaleCondition , LotArea , YearBuilt , OverallCond , MasVnrArea , 
    PoolQC , BedroomAbvGr , GarageCars , MasVnrType , TotalBsmtSF , 
    BldgType , Functional , ExterQual , BsmtCond , Condition1 , 
    Exterior1st , MoSold , GarageCond , ScreenPorch , LandContour , 
    LowQualFinSF , LotConfig , LotFrontage , TotRmsAbvGrd , KitchenAbvGr , 
    WoodDeckSF , Street , GarageArea , LotShape , BsmtQual , 
    Fireplaces , FireplaceQu , PoolArea , RoofStyle , BsmtFinSF2 , 
    Utilities , ExterCond)


### Backwards Elimination results - Option 2.

Model 2: SalePrice ~ LotFrontage + LotArea + Street + LotShape + LandContour + 
    Utilities + LotConfig + Neighborhood + Condition1 + Condition2 + 
    BldgType + HouseStyle + OverallQual + OverallCond + YearBuilt + 
    RoofMatl + Exterior1st + MasVnrType + MasVnrArea + ExterQual + 
    ExterCond + Foundation + BsmtQual + BsmtCond + BsmtExposure + 
    BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF + X1stFlrSF + X2ndFlrSF + 
    HalfBath + BedroomAbvGr + KitchenAbvGr + KitchenQual + TotRmsAbvGrd + 
    Functional + Fireplaces + FireplaceQu + GarageType + GarageCars + 
    GarageArea + WoodDeckSF + X3SsnPorch + ScreenPorch + PoolQC + 
    Fence + MiscFeature + MoSold + SaleCondition    
    
c(LotFrontage , LotArea , Street , LotShape , LandContour , 
    Utilities , LotConfig , Neighborhood , Condition1 , Condition2 , 
    BldgType , HouseStyle , OverallQual , OverallCond , YearBuilt , 
    RoofMatl , Exterior1st , MasVnrType , MasVnrArea , ExterQual , 
    ExterCond , Foundation , BsmtQual , BsmtCond , BsmtExposure , 
    BsmtFinSF1 , BsmtFinSF2 , BsmtUnfSF , X1stFlrSF , X2ndFlrSF , 
    HalfBath , BedroomAbvGr , KitchenAbvGr , KitchenQual , TotRmsAbvGrd , 
    Functional , Fireplaces , FireplaceQu , GarageType , GarageCars , 
    GarageArea , WoodDeckSF , X3SsnPorch , ScreenPorch , PoolQC , 
    Fence , MiscFeature , MoSold , SaleCondition)



#### Selected Feature from Boruta - Random forest selection - Option 3

MSSubClass+MSZoning+LotFrontage+LotArea+Alley+LotShape+LandContour+LandSlope+Neighborhood+
BldgType+HouseStyle+OverallQual+OverallCond+YearBuilt+YearRemodAdd+RoofStyle+Exterior1st+Exterior2nd+
MasVnrType+MasVnrArea+ExterQual+Foundation+BsmtQual+BsmtCond+BsmtExposure+BsmtFinType1+BsmtFinSF1+
BsmtFinType2+BsmtUnfSF+TotalBsmtSF+HeatingQC+CentralAir+X1stFlrSF+X2ndFlrSF+GrLivArea+BsmtFullBath+
FullBath+HalfBath+BedroomAbvGr+KitchenAbvGr+KitchenQual+TotRmsAbvGrd+Fireplaces+FireplaceQu+GarageType+
GarageYrBlt+GarageFinish+GarageCars+GarageArea+GarageQual+GarageCond+PavedDrive+WoodDeckSF+OpenPorchSF

c(MSSubClass,MSZoning,LotFrontage,LotArea,Alley,LotShape,LandContour,LandSlope,Neighborhood,
BldgType,HouseStyle,OverallQual,OverallCond,YearBuilt,YearRemodAdd,RoofStyle,Exterior1st,Exterior2nd,
MasVnrType,MasVnrArea,ExterQual,Foundation,BsmtQual,BsmtCond,BsmtExposure,BsmtFinType1,BsmtFinSF1,
BsmtFinType2,BsmtUnfSF,TotalBsmtSF,HeatingQC,CentralAir,X1stFlrSF,X2ndFlrSF,GrLivArea,BsmtFullBath,
FullBath,HalfBath,BedroomAbvGr,KitchenAbvGr,KitchenQual,TotRmsAbvGrd,Fireplaces,FireplaceQu,GarageType,
GarageYrBlt,GarageFinish,GarageCars,GarageArea,GarageQual,GarageCond,PavedDrive,WoodDeckSF,OpenPorchSF)


```{r}
#MyIndex<-sample(2,nrow(Train),replace=T,prob=c(0.7,0.3))
```
#### Linear Regression

```{r}

#All
myLm1<-lm(SalePrice~.,data=Train) # All

myLm2<-lm(SalePrice ~ OverallQual + GrLivArea + Neighborhood + BsmtFinSF1 + 
    RoofMatl + MSSubClass + BsmtExposure + KitchenQual + Condition2 + 
    SaleCondition + LotArea + YearBuilt + OverallCond + MasVnrArea + 
    PoolQC + BedroomAbvGr + GarageCars + MasVnrType + TotalBsmtSF + 
    BldgType + Functional + ExterQual + BsmtCond + Condition1 + 
    Exterior1st + MoSold + GarageCond + ScreenPorch + LandContour + 
    LowQualFinSF + LotConfig + LotFrontage + TotRmsAbvGrd + KitchenAbvGr + 
    WoodDeckSF + Street + GarageArea + LotShape + BsmtQual + 
    Fireplaces + FireplaceQu + PoolArea + RoofStyle + BsmtFinSF2 + 
    Utilities + ExterCond, data = Train)
myLm3<-lm(SalePrice ~ LotFrontage + LotArea + Street + LotShape + LandContour + 
    Utilities + LotConfig + Neighborhood + Condition1 + Condition2 + 
    BldgType + HouseStyle + OverallQual + OverallCond + YearBuilt + 
    RoofMatl + Exterior1st + MasVnrType + MasVnrArea + ExterQual + 
    ExterCond + Foundation + BsmtQual + BsmtCond + BsmtExposure + 
    BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF + X1stFlrSF + X2ndFlrSF + 
    HalfBath + BedroomAbvGr + KitchenAbvGr + KitchenQual + TotRmsAbvGrd + 
    Functional + Fireplaces + FireplaceQu + GarageType + GarageCars + 
    GarageArea + WoodDeckSF + X3SsnPorch + ScreenPorch + PoolQC + 
    Fence + MiscFeature + MoSold + SaleCondition    , data = Train)
myLm4<-lm(SalePrice ~ MSSubClass+MSZoning+LotFrontage+LotArea+Alley+LotShape+LandContour+LandSlope+Neighborhood+
BldgType+HouseStyle+OverallQual+OverallCond+YearBuilt+YearRemodAdd+RoofStyle+Exterior1st+Exterior2nd+
MasVnrType+MasVnrArea+ExterQual+Foundation+BsmtQual+BsmtCond+BsmtExposure+BsmtFinType1+BsmtFinSF1+
BsmtFinType2+BsmtUnfSF+TotalBsmtSF+HeatingQC+CentralAir+X1stFlrSF+X2ndFlrSF+GrLivArea+BsmtFullBath+
FullBath+HalfBath+BedroomAbvGr+KitchenAbvGr+KitchenQual+TotRmsAbvGrd+Fireplaces+FireplaceQu+GarageType+
GarageYrBlt+GarageFinish+GarageCars+GarageArea+GarageQual+GarageCond+PavedDrive+WoodDeckSF+OpenPorchSF
,data=Train)



summary(myLm1)
summary(myLm2)
summary(myLm3)
summary(myLm4)


```



```{r}
par(mfrow=c(2,2))
plot(myLm1)
plot(myLm2)
plot(myLm3)
plot(myLm4)

plot(myLm1,which=c(4))
plot(myLm2,which=c(4))
plot(myLm3,which=c(4))
plot(myLm4,which=c(4))

```
Where all linear feature selection shows 524, 826 1183 as outlier, random forest selection chooses 1299 more of a problem than 524 or 1183.

##### Prediction using all 4 linear models
```{r}
pd1<-predict(myLm1,interval='prediction',newdata=Test)
pd2<-predict(myLm2,interval='prediction',newdata=Test)
pd3<-predict(myLm3,interval='prediction',newdata=Test)
pd4<-predict(myLm4,interval='prediction',newdata=Test)

```
##### Prediction VS Actual plot 
##### RMSLE / RMSE calculated for test set.
```{r}
act<-read.csv( file = "C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\AMES_test.csv")
actual<-act[1461:2919,2]
par(mfrow=c(2,2))
plot(actual,pd1[,1],pch=3)
plot(actual,pd2[,1],pch=3, col='blue')
plot(actual,pd3[,1],pch=3, col='red')
plot(actual,pd4[,1],pch=3, col='green')

RMSLE(pd1[,1],actual)
RMSLE(pd2[,1],actual)
RMSLE(pd3[,1],actual)
RMSLE(pd4[,1],actual)


RMSE(pd1[,1],actual)
RMSE(pd2[,1],actual)
RMSE(pd3[,1],actual)
RMSE(pd4[,1],actual)



```
#### Random Forest 
RF1<-RandomForest()

```{r}
RF1<-randomForest(SalePrice~.,data=Train)

RF2<-randomForest(SalePrice ~ OverallQual + GrLivArea + Neighborhood + BsmtFinSF1 + 
    RoofMatl + MSSubClass + BsmtExposure + KitchenQual + Condition2 + 
    SaleCondition + LotArea + YearBuilt + OverallCond + MasVnrArea + 
    PoolQC + BedroomAbvGr + GarageCars + MasVnrType + TotalBsmtSF + 
    BldgType + Functional + ExterQual + BsmtCond + Condition1 + 
    Exterior1st + MoSold + GarageCond + ScreenPorch + LandContour + 
    LowQualFinSF + LotConfig + LotFrontage + TotRmsAbvGrd + KitchenAbvGr + 
    WoodDeckSF + Street + GarageArea + LotShape + BsmtQual + 
    Fireplaces + FireplaceQu + PoolArea + RoofStyle + BsmtFinSF2 + 
    Utilities + ExterCond, data = Train)
RF3<-randomForest(SalePrice ~ LotFrontage + LotArea + Street + LotShape + LandContour + 
    Utilities + LotConfig + Neighborhood + Condition1 + Condition2 + 
    BldgType + HouseStyle + OverallQual + OverallCond + YearBuilt + 
    RoofMatl + Exterior1st + MasVnrType + MasVnrArea + ExterQual + 
    ExterCond + Foundation + BsmtQual + BsmtCond + BsmtExposure + 
    BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF + X1stFlrSF + X2ndFlrSF + 
    HalfBath + BedroomAbvGr + KitchenAbvGr + KitchenQual + TotRmsAbvGrd + 
    Functional + Fireplaces + FireplaceQu + GarageType + GarageCars + 
    GarageArea + WoodDeckSF + X3SsnPorch + ScreenPorch + PoolQC + 
    Fence + MiscFeature + MoSold + SaleCondition    , data = Train)
RF4<-randomForest(SalePrice ~ MSSubClass+MSZoning+LotFrontage+LotArea+Alley+LotShape+LandContour+LandSlope+Neighborhood+
BldgType+HouseStyle+OverallQual+OverallCond+YearBuilt+YearRemodAdd+RoofStyle+Exterior1st+Exterior2nd+
MasVnrType+MasVnrArea+ExterQual+Foundation+BsmtQual+BsmtCond+BsmtExposure+BsmtFinType1+BsmtFinSF1+
BsmtFinType2+BsmtUnfSF+TotalBsmtSF+HeatingQC+CentralAir+X1stFlrSF+X2ndFlrSF+GrLivArea+BsmtFullBath+
FullBath+HalfBath+BedroomAbvGr+KitchenAbvGr+KitchenQual+TotRmsAbvGrd+Fireplaces+FireplaceQu+GarageType+
GarageYrBlt+GarageFinish+GarageCars+GarageArea+GarageQual+GarageCond+PavedDrive+WoodDeckSF+OpenPorchSF
,data=Train)



summary(myLm1)
summary(myLm2)
summary(myLm3)
summary(myLm4)
```
Some coefficients not defined due to singularities.

#### Prediction with Random Forest
```{r}
pdRF1<-predict(RF1,interval='prediction',newdata=Test)
pdRF2<-predict(RF2,interval='prediction',newdata=Test)
pdRF3<-predict(RF3,interval='prediction',newdata=Test)
pdRF4<-predict(RF4,interval='prediction',newdata=Test)

par(mfrow=c(2,2))
plot(actual,pdRF1,pch=3, main='Prediction VS Actual, all var')
plot(actual,pdRF2,pch=3, col='blue',main='Prediction VS Actual, FowardSelect')
plot(actual,pdRF3,pch=3, col='red',main='Prediction VS Actual, Backwards Elim')
plot(actual,pdRF4,pch=3, col='green',main='Prediction VS Actual, Boruta')

RMSLE(pdRF1,actual)
RMSLE(pdRF2,actual)
RMSLE(pdRF3,actual)
RMSLE(pdRF4,actual)

RMSE(pdRF1,actual)
RMSE(pdRF2,actual)
RMSE(pdRF3,actual)
RMSE(pdRF4,actual)
```


#### SV Regression
model <- svm(Y ~ X , data)
```{r}
SV1<-svm(SalePrice~.,data=Train, cost=4)


SV2<-svm(SalePrice ~ OverallQual + GrLivArea + Neighborhood + BsmtFinSF1 + 
    RoofMatl + MSSubClass + BsmtExposure + KitchenQual + Condition2 + 
    SaleCondition + LotArea + YearBuilt + OverallCond + MasVnrArea + 
    PoolQC + BedroomAbvGr + GarageCars + MasVnrType + TotalBsmtSF + 
    BldgType + Functional + ExterQual + BsmtCond + Condition1 + 
    Exterior1st + MoSold + GarageCond + ScreenPorch + LandContour + 
    LowQualFinSF + LotConfig + LotFrontage + TotRmsAbvGrd + KitchenAbvGr + 
    WoodDeckSF + Street + GarageArea + LotShape + BsmtQual + 
    Fireplaces + FireplaceQu + PoolArea + RoofStyle + BsmtFinSF2 + 
    Utilities + ExterCond, data=Train, cost=4)


SV3<-svm(SalePrice ~ LotFrontage + LotArea + Street + LotShape + LandContour + 
    Utilities + LotConfig + Neighborhood + Condition1 + Condition2 + 
    BldgType + HouseStyle + OverallQual + OverallCond + YearBuilt + 
    RoofMatl + Exterior1st + MasVnrType + MasVnrArea + ExterQual + 
    ExterCond + Foundation + BsmtQual + BsmtCond + BsmtExposure + 
    BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF + X1stFlrSF + X2ndFlrSF + 
    HalfBath + BedroomAbvGr + KitchenAbvGr + KitchenQual + TotRmsAbvGrd + 
    Functional + Fireplaces + FireplaceQu + GarageType + GarageCars + 
    GarageArea + WoodDeckSF + X3SsnPorch + ScreenPorch + PoolQC + 
    Fence + MiscFeature + MoSold + SaleCondition, data=Train, cost=4)    
    
SV4<-svm(SalePrice~MSSubClass+MSZoning+LotFrontage+LotArea+Alley+LotShape+LandContour+LandSlope+Neighborhood+
BldgType+HouseStyle+OverallQual+OverallCond+YearBuilt+YearRemodAdd+RoofStyle+Exterior1st+Exterior2nd+
MasVnrType+MasVnrArea+ExterQual+Foundation+BsmtQual+BsmtCond+BsmtExposure+BsmtFinType1+BsmtFinSF1+
BsmtFinType2+BsmtUnfSF+TotalBsmtSF+HeatingQC+CentralAir+X1stFlrSF+X2ndFlrSF+GrLivArea+BsmtFullBath+
FullBath+HalfBath+BedroomAbvGr+KitchenAbvGr+KitchenQual+TotRmsAbvGrd+Fireplaces+FireplaceQu+GarageType+
GarageYrBlt+GarageFinish+GarageCars+GarageArea+GarageQual+GarageCond+PavedDrive+WoodDeckSF+OpenPorchSF, data=Train, cost=4)


pdSV1<-predict(SV1,newdata=Test[,-80])
pdSV2<-predict(SV2,newdata=Test[,-80])
pdSV3<-predict(SV3,newdata=Test[,-80])
pdSV4<-predict(SV4,newdata=Test[,-80])

summary(SV1)
par(mfrow=c(2,2))
plot(actual,pdSV1,pch=3, main='Prediction VS Actual, all var')
plot(actual,pdSV2,pch=3, col='blue',main='Prediction VS Actual, FowardSelect')
plot(actual,pdSV3,pch=3, col='red',main='Prediction VS Actual, Backwards Elim')
plot(actual,pdSV4,pch=3, col='green',main='Prediction VS Actual, Boruta')

RMSLE(pdSV1,actual)
RMSLE(pdSV2,actual)
RMSLE(pdSV3,actual)
RMSLE(pdSV4,actual)

RMSE(pdSV1,actual)
RMSE(pdRF2,actual)
RMSE(pdRF3,actual)
RMSE(pdRF4,actual)
```
#### Looking at below comparison, overall SVM > Random Forest > OLS.

It looks like the SVM is showing the best result oddly enough with all variables then followed by Boruta selection. This could be because the dataset has many none normal distributions, has colinearity issues, and variance is not consistent and thus is not perfect candidate for using linear regression. I will transform some skewed items to log scale and try linear fit again to fine tune and also will tune SVM and Random forest to acheive better results.  

Model 1
RMLSE [1] 0.1837928 VS [1] 0.1436806 [1] 0.1287456
RMSE  [1] 29630.08  VS [1] 23335.57 [1] 21198.8

Model 2 
[1] 0.1636028 VS [1] 0.1446042 [1] 0.1323565
[1] 28584.97 VS [1] 23778.01 [1] 23668.95

Model 3 
[1] 0.1769506 VS  [1] 0.1508996 [1] 0.134205
[1] 28721.35 VS [1] 24579.31 [1] 24408.31

Model 4
[1] 0.1735936 VS [1] 0.1436703 [1] 0.1299854
[1] 27252.57 VS [1] 23337.88 1] 23437.68


#### BELOW NOT READY ####
#### Regularization Method ####


myLm<-train(
  SalePrice ~., data = Train,
  method='lm', trControl=Mycontrols)



#Lasso

```{r, eval=F}
myLasso1 <-train(SalePrice~.,
                 data = Train
                 ,method='glmnet',
                 tuneGrid=expand.grid(alpha=1,lambda=seq(500,1500,length=100)), trControl=Mycontrols)
myLasso2 <-train(
  SalePrice ~ OverallQual + GrLivArea + Neighborhood + 
    BsmtFinSF1 + RoofMatl + MSSubClass + BsmtExposure + KitchenQual + 
    Condition2 + SaleCondition + LotArea + YearBuilt + OverallCond + 
    MasVnrArea + PoolQC + BedroomAbvGr + GarageCars + GarageFinish + 
    TotalBsmtSF + BldgType + MasVnrType + Functional + ExterQual + 
    BsmtCond + Condition1 + Exterior1st + LandContour + MoSold + 
    ScreenPorch + LowQualFinSF + LotConfig + LotFrontage + WoodDeckSF + 
    Street + GarageArea + KitchenAbvGr + TotRmsAbvGrd + LotShape + 
    ExterCond + PoolArea + BsmtFinSF2 + Fireplaces + FireplaceQu + 
    BsmtQual + X3SsnPorch + Foundation + Utilities, data = Train
  ,method='glmnet',tuneGrid=expand.grid(alpha=1,lambda=seq(500,1500,length=100)), trControl=Mycontrols)


```




```{r, eval=F}
plot(myLasso1)
plot(varImp(myLasso1), Scale=F)
varImp(myLasso1)
myLasso1$bestTune
myLasso1
plot(myLasso1$finalModel)
coef(myLasso1)

plot(myLasso2)
plot(varImp(myLasso2), Scale=F)
varImp(myLasso2)
myLasso2$bestTune
myLasso2
plot(myLasso2$finalModel)
coef(myLasso2)
```

## Elasticnet


myEla<-train(SalePrice~.,Train,method='glmnet',tuneGrid=expand.grid(alpha=seq(0, 1,length=10),lambda=seq(0.0001,2000,length=20)), trControl=Mycontrols)

plot(myEla)
plot(varImp(myEla))
varImp(myEla)
myEla$bestTune
myEla
```

