---
title: "136_Liz_Project_Step5_SVM Playground"
author: "Hyunkyung Kim"
date: "December 4, 2018"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
#install.packages("glmnet")
#install.packages("mlbench")
#install.packages("Boruta")
library(caret)
library(tidyverse)
library(psych)
library(glmnet)
library(mlbench)
library(Boruta)
library(MASS) # stepwise regression
library(leaps) # all subsets regression
library(randomForest)
library(MLmetrics)
library(e1071)
```

### Import Cleaned Data

```{r}

H_Clean<-read.csv( file = "C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\H_clean.csv")

Train<-H_Clean[!is.na(H_Clean$SalePrice),-1] #Remove ID
Test<-H_Clean[is.na(H_Clean$SalePrice),-1] 
actual<-read.csv( file = "C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\AMES_test.csv")[1461:2919,2] # Test Price
#Remove Utilities - only one exception and is causing issues. Also will result in huge variance

tc<-trainControl(method="cv", number=10)

Train11<-Train[,names(Train)!="Utilities"]
```




```{r}
f2<-SalePrice ~ OverallQual + GrLivArea + Neighborhood + BsmtFinSF1 + 
    RoofMatl + MSSubClass + BsmtExposure + KitchenQual + Condition2 + 
    SaleCondition + LotArea + YearBuilt + OverallCond + MasVnrArea + 
    PoolQC + BedroomAbvGr + GarageCars + MasVnrType + TotalBsmtSF + 
    BldgType + Functional + ExterQual + BsmtCond + Condition1 + 
    Exterior1st + MoSold + GarageCond + ScreenPorch + LandContour + 
    LowQualFinSF + LotConfig + LotFrontage + TotRmsAbvGrd + KitchenAbvGr + 
    WoodDeckSF + Street + GarageArea + LotShape + BsmtQual + 
    Fireplaces + FireplaceQu + PoolArea + RoofStyle + BsmtFinSF2 + 
     ExterCond # Utilities Removed
f3<- SalePrice ~ LotFrontage + LotArea + Street + LotShape + LandContour + 
    + LotConfig + Neighborhood + Condition1 + Condition2 + 
    BldgType + HouseStyle + OverallQual + OverallCond + YearBuilt + 
    RoofMatl + Exterior1st + MasVnrType + MasVnrArea + ExterQual + 
    ExterCond + Foundation + BsmtQual + BsmtCond + BsmtExposure + 
    BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF + X1stFlrSF + X2ndFlrSF + 
    HalfBath + BedroomAbvGr + KitchenAbvGr + KitchenQual + TotRmsAbvGrd + 
    Functional + Fireplaces + FireplaceQu + GarageType + GarageCars + 
    GarageArea + WoodDeckSF + X3SsnPorch + ScreenPorch + PoolQC + 
    Fence + MiscFeature + MoSold + SaleCondition    # Utilities Removed - because tuning was done without it - error otherwise.

f4<-SalePrice ~MSSubClass+MSZoning+LotFrontage+LotArea+Alley+LotShape+LandContour+LandSlope+Neighborhood+
BldgType+HouseStyle+OverallQual+OverallCond+YearBuilt+YearRemodAdd+RoofStyle+Exterior1st+Exterior2nd+
MasVnrType+MasVnrArea+ExterQual+Foundation+BsmtQual+BsmtCond+BsmtExposure+BsmtFinType1+BsmtFinSF1+
BsmtFinType2+BsmtUnfSF+TotalBsmtSF+HeatingQC+CentralAir+X1stFlrSF+X2ndFlrSF+GrLivArea+BsmtFullBath+
FullBath+HalfBath+BedroomAbvGr+KitchenAbvGr+KitchenQual+TotRmsAbvGrd+Fireplaces+FireplaceQu+GarageType+
GarageYrBlt+GarageFinish+GarageCars+GarageArea+GarageQual+GarageCond+PavedDrive+WoodDeckSF+OpenPorchSF

```


Radial SVM - best tuned without big anomalies. 524, 1299
```{r}
SV1<-svm(SalePrice~.,data=Train11, cost=2.25, gamma=0.0035)
SV2<-svm(SalePrice~.,data=Train11[-c(524,1299),], cost=2.25, gamma=0.0035)
#SV2<-svm(f2,data=Train,cost=4)
SV3<-svm(f4,data=Train11[-c(524,1299),],gamma= 0.007,  cost=1.5, espilon=0.06)    
SV4<-svm(f4, data=Train11[,], cost=1.5, gamma=0.007, epsilon=0.06)




pdSV1<-predict(SV1,newdata=Test[,-80])
pdSV2<-predict(SV2,newdata=Test[,-80])
pdSV3<-predict(SV3,newdata=Test[,-80])
pdSV4<-predict(SV4,newdata=Test[,-80])



summary(SV1)
par(mfrow=c(1,2))
plot(actual,pdSV2,pch=3, col='blue',main='Pred VS Actual, All var, outlier Rmv')
abline(a=0,b=1)
plot(log(actual),log(pdSV2),pch=3, col='blue',main='Pred VS Actual, All var, outlier Rmv')
abline(a=0,b=1)

plot(actual,pdSV1,pch=3, main='Pred VS Actual, All var')
abline(a=0,b=1)
plot(actual,pdSV2,pch=3, col='blue',main='Pred VS Actual, All var, outlier Rmv')
abline(a=0,b=1)
plot(actual,pdSV3,pch=3, col='red',main='Pred VS Actual,Boruta')
abline(a=0,b=1)
plot(actual,pdSV4,pch=3, col='green',main='Pred VS Actual,Boruta , Outlier Rmv')
abline(a=0,b=1)



print("Test RMSLE & RMSE")
RMSE(log(pdSV1),log(actual))
RMSE(log(pdSV2),log(actual))
RMSE(log(pdSV3),log(actual))
RMSE(log(pdSV4),log(actual))
RMSLE(pdSV1,actual)
RMSLE(pdSV2,actual)
RMSLE(pdSV3,actual)
RMSLE(pdSV4,actual)

#RMSE(pdSV1,actual)
#RMSE(pdSV2,actual)
#RMSE(pdSV3,actual)
#RMSE(pdSV4,actual)
```

[1] "Test RMSLE & RMSE" - epsilon not defined
[1] 0.1236311
[1] 0.1239871
[1] 0.1280652
[1] 0.127133

[1] "Test RMSLE & RMSE" - epsilon 0.06
[1] 0.1239504
[1] 0.1241208
[1] 0.1280652
[1] 0.1259828



Linear SVM Using Radial Tuned SVM parameters

```{r}
SVl1<-svm(SalePrice~.,data=Train11, cost=2.25, epsilon=0.06,kernel='linear')
SVl2<-svm(f2,data=Train11,epsilon=0.06, cost=2.25,kernel='linear')
SVl3<-svm(f3,data=Train11,cost=2.25, epsilon=0.06,kernel='linear')  
SVl4<-svm(f4, data=Train11,cost=1.5,  epsilon=0.06, kernel='linear')


pdSVl1<-predict(SVl1,newdata=Test[,-80])
pdSVl2<-predict(SVl2,newdata=Test[,-80])
pdSVl3<-predict(SVl3,newdata=Test[,-80])
pdSVl4<-predict(SVl4,newdata=Test[,-80])

pdSVl01<-predict(SVl1,newdata=Train[,-80])
pdSVl02<-predict(SVl2,newdata=Train[,-80])
pdSVl03<-predict(SVl3,newdata=Train[,-80])
pdSVl04<-predict(SVl4,newdata=Train[,-80])


summary(SVl1)
par(mfrow=c(1,2))
plot(actual,pdSVl1,pch=3, main='Prediction VS Actual, all var')
abline(a=0,b=1)
#plot(actual,pdSVl2,pch=3, col='blue',main='Pred VS Actual, FowardSelect')
#abline(a=0,b=1)
plot(actual,pdSVl3,pch=3, col='red',main='Pred VS Actual, BackwardElim')
abline(a=0,b=1)
plot(actual,pdSVl4,pch=3, col='green',main='Pred VS Actual, Boruta')
abline(a=0,b=1)
```

```{r}

print("Test RMSLE " )
RMSLE(pdSVl1,actual)
RMSLE(pdSVl2,actual)
RMSLE(pdSVl3,actual)
RMSLE(pdSVl4,actual)

```
Train[,names(Train)!="Utilities"]
#### POLYNOMIAL SVM

Degree =2 

```{r}
SVp1<-svm(SalePrice~.,data=Train11, cost=2.25, gamma=  0.0035, degree=2, kernel='polynomial')
SVp2<-svm(f2,data=Train11, cost=2.25,degree=2, gamma=  0.0035,kernel='polynomial')
SVp3<-svm(f3,data=Train11,cost=2.25 ,degree=2,gamma=  0.0035, kernel='polynomial')
SVp4<-svm(f4,data=Train11,cost=1.5, degree=2,gamma=  0.007, kernel='polynomial')


pdSVp1<-predict(SVp1,newdata=Test[,-80])
pdSVp2<-predict(SVp2,newdata=Test[,-80])
pdSVp3<-predict(SVp3,newdata=Test[,-80])
pdSVp4<-predict(SVp4,newdata=Test[,-80])


summary(SVp1)
summary(SVp2)
```





```{r}
par(mfrow=c(1,2))
plot(actual,pdSVp1,pch=3, main='Prediction VS Actual, all var')
abline(a=0,b=1)
plot(actual,pdSVp2,pch=3, col='blue',main='Prediction VS Actual, FowardSelect')
abline(a=0,b=1)
plot(actual,pdSVp3,pch=3, col='red',main='Prediction VS Actual, Backwards Elim')
abline(a=0,b=1)
plot(actual,pdSVp4,pch=3, col='green',main='Prediction VS Actual, Boruta')
abline(a=0,b=1)

print("Test RMSLE")
RMSLE(pdSVp1,actual)
RMSLE(pdSVp2,actual)
RMSLE(pdSVp3,actual)
RMSLE(pdSVp4,actual)

```
Have issue with one point that is low price but prediced high for all. This is a very big difference. Would like to investigate this.

Polynomial with degree 3 (default)
```{r}
SVp31<-svm(SalePrice~.,data=Train11, cost=2.25, gamma=  0.0035, kernel='polynomial')
SVp32<-svm(f2,data=Train11, cost=2.25, gamma=  0.0035,kernel='polynomial')
SVp33<-svm(f3,data=Train11,cost=2.25 ,gamma=  0.0035, kernel='polynomial')
SVp34<-svm(f4,data=Train11,cost=1.5, gamma=  0.007, kernel='polynomial')


pdSVp31<-predict(SVp31,newdata=Test[,-80])
pdSVp32<-predict(SVp32,newdata=Test[,-80])
pdSVp33<-predict(SVp33,newdata=Test[,-80])
pdSVp34<-predict(SVp34,newdata=Test[,-80])

#pdSVl1101<-predict(SVl111,newdata=Train[,-80])
#pdSVl1102<-predict(SVl112,newdata=Train[,-80])
#pdSVl1103<-predict(SVl113,newdata=Train[,-80])
#pdSVl1104<-predict(SVl114,newdata=Train[,-80])


summary(SVp31)
summary(SVp32)
```

```{r}
par(mfrow=c(1,2))
plot(actual,pdSVp33,pch=3, col='red',main='Prediction VS Actual, Backwards Elim')
abline(a=0,b=1)
plot(actual,pdSVp34,pch=3, col='green',main='Prediction VS Actual, Boruta')
abline(a=0,b=1)
plot(actual,pdSVp31,pch=3, main='Prediction VS Actual, all var')
abline(a=0,b=1)
plot(actual,pdSVp32,pch=3, col='blue',main='Prediction VS Actual, FowardSelect')
abline(a=0,b=1)


print("Test RMSLE")
RMSLE(pdSVp31,actual)
RMSLE(pdSVp32,actual)
RMSLE(pdSVp33,actual)
RMSLE(pdSVp34,actual)


```

SVM - Sigmoid
```{r}
SVs1<-svm(SalePrice~.,data=Train11, cost=2.25, gamma=  0.0035, kernel='sigmoid')
SVs2<-svm(f2,data=Train11, cost=2.25, gamma=  0.0035,kernel='sigmoid')
SVs3<-svm(f3,data=Train11,cost=2.25 ,gamma=  0.0035, kernel='sigmoid')
SVs4<-svm(f4,data=Train11,cost=1.5, gamma=  0.007, kernel='sigmoid')


pdSVs1<-predict(SVs1,newdata=Test[,-80])
pdSVs2<-predict(SVs2,newdata=Test[,-80])
pdSVs3<-predict(SVs3,newdata=Test[,-80])
pdSVs4<-predict(SVs4,newdata=Test[,-80])

#pdSVl1101<-predict(SVl111,newdata=Train[,-80])
#pdSVl1102<-predict(SVl112,newdata=Train[,-80])
#pdSVl1103<-predict(SVl113,newdata=Train[,-80])
#pdSVl1104<-predict(SVl114,newdata=Train[,-80])


summary(SVs1)
summary(SVs2)
```
SVM - Sigmoid : Disaster. RMSE cannot be calculated.
```{r}
par(mfrow=c(1,2))
plot(actual,pdSVs1,pch=3, col='red',main='Prediction VS Actual, Backwards Elim')
abline(a=0,b=1)
plot(actual,pdSVs2,pch=3, col='green',main='Prediction VS Actual, Boruta')
abline(a=0,b=1)
plot(actual,pdSVs3,pch=3, main='Prediction VS Actual, all var')
abline(a=0,b=1)
plot(actual,pdSVs4,pch=3, col='blue',main='Prediction VS Actual, FowardSelect')
abline(a=0,b=1)


print("Test RMSLE")
RMSLE(pdSVs1,actual)
RMSLE(pdSVs2,actual)
RMSLE(pdSVs3,actual)
RMSLE(pdSVs4,actual)


```


TUNING FOR LINEAR DO NOT RUN

```{r, eval=F}
SV_Lin_tune1<-tune.svm(SalePrice~.,data=Train11,cost=c(20,10,1), kernel='linear')
```


```{r, eval=F}
plot(SV_Lin_tune1)
```




```{r, eval=F}
print(SV_Lin_tune1)
sqrt(SV_Lin_tune1$best.performance)
```

```{r, eval=F}
SV_Lin_tune2<-tune.svm(SalePrice~.,data=Train11,cost=c(5,0.5), kernel='linear')
```


```{r, eval=F}
Train11<-Train[,names(Train)!='Utilities']
SV_Lin_tune12<-tune.svm(SalePrice~.,data=Train11,cost=seq(1,21,2),gamma=seq(1,21,2))
```


```{r, eval=F}
plot(SV_Lin_tune12)
```



```{r, eval=F}
print(SV_Lin_tune12)
sqrt(SV_Lin_tune12$best.performance)
```

```{r, eval=F}
SV_Lin_tune13<-tune.svm(SalePrice~.,data=Train11,cost=c(2,5,0.5),gamma=seq(0.5,1.5,0.1))
```

