---
title: "Project_HousePrediction_Data Exploration"
author: "Hyunkyung Kim"
date: "October 11, 2018"
output: word_document
---

```{r}
#install.packages("caret")
#install.packages("dplyr")
library(caret)
library(dplyr)

library(leaps)
```

## Import Data and Save a Copy##
housedata - original data
housedatac - working copy of the data

```{r}
housedata<-read.csv("C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\train.csv")
housedatac<-housedata

```

## Investigating the variables.
## Checking # of N/A data 

```{r}
str(housedata)

```
## Checking for duplicates & uniques : Both 1460 rows - meaning No duplicate
## Display features that has non zero N/As.

```{r}

nrow(housedata)
nrow(unique(housedata))

NAs<-colSums(is.na(housedata))
NAs[NAs>0]

```
## Number of rows = # of unique rows : no duplicate data
## Features that has N/As are displayed - Will work with that.



## Data Description ##
Checking Min/Max/quartiles for numerical, and table for categorical variables.
```{r}
summary(housedata)
```
## Data Visualization & basic transformation##
## Before this, going to do some basic data cleaning ##


## CLEANING DATA ##

#1. Remove ID
ID is not really relative data here. It just identifies the rows.
```{r}
housedatac<-select(housedatac, -c(Id))
```


# 2. MSSubClass to factor.
MSSubclass is actually categorical - represented as numeric. Need to change to factor.
```{r}
housedatac$MSSubClass<-as.factor(housedatac$MSSubClass)
```

MSSubClass: Identifies the type of dwelling involved in the sale.	
	
20	1-STORY 1946 & NEWER ALL STYLES
30	1-STORY 1945 & OLDER
40	1-STORY W/FINISHED ATTIC ALL AGES
45	1-1/2 STORY - UNFINISHED ALL AGES
50	1-1/2 STORY FINISHED ALL AGES
60	2-STORY 1946 & NEWER
70	2-STORY 1945 & OLDER
75	2-1/2 STORY ALL AGES
80	SPLIT OR MULTI-LEVEL
85	SPLIT FOYER
90	DUPLEX - ALL STYLES AND AGES
120	1-STORY PUD (Planned Unit Development) - 1946 & NEWER
150	1-1/2 STORY PUD - ALL AGES
160	2-STORY PUD - 1946 & NEWER
180	PUD - MULTILEVEL - INCL SPLIT LEV/FOYER
190	2 FAMILY CONVERSION - ALL STYLES AND AGES

# Dividing into numerical and categorical columns to visualize some data.

# Numerical

```{r}

# Numerical into nums
nums <- unlist(lapply(housedatac, is.numeric))  
housedata_num<-housedatac[ , nums]

colnames(housedata_num)




```

# Categorical
```{r}
# Categorical into cat. 

cats <-unlist(lapply(housedatac,is.factor))
housedata_cat<-housedatac[,cats]



colnames(housedata_cat)
```




# Initial Plots for Numerical Data




## Plot numerical - Histogram ##
```{r, echo=FALSE}
#sapply(housedata_num, hist,main=colnames(housedata_num), )
par(mfrow=c(2,3))
mapply(hist,as.data.frame(housedata_num),main=colnames(housedata_num),xlab='' ,breaks=20, col="blue")


```

## Plot numerical 2 - Boxplot ## 
```{r}
par(mfrow=c(2,5))
# Where does this c(1:10) come from?

mapply(boxplot,data.frame(housedata_num[,c(1:12)]),main=colnames(housedata_num))
```


## Plot Categorical - Bar Plot ##

```{r}
# par(mfrow=c(1,2))
# Barplots needs to be in table first in order to plot.
for (i in 1:44)
(

barplot(table(housedata_cat[,i],useNA="ifany"), col="red", las=2, main=colnames(housedata_cat[i]))
)
```






























***  missing data ***
Remove VS Impute?: 
Column	# of NA

Alley	1369
PoolQC	1453
Fence	1179
MiscFeature	1406
FireplaceQu	690


1. Option 1 -opt1h_cat 
Remove. Alley  to MiscFeature  - The
```{r}

opt1h_cat

opt2h_cat


```



# In order to add new level, 
levels(x)<-c(levels(x),"None")  #Add the extra level to your factor
x[is.na(x)] <- "None"  
```{r}
levels(housedata_cat$Alley)<-c(levels(housedata_cat$Alley),"NoAlley")
housedata_cat$Alley[is.na(housedata_cat$Alley)]<-"NoAlley"
table(housedata_cat$Alley)

levels(housedata_cat$PoolQC)<-c(levels(housedata_cat$PoolQC),"NoPool")
housedata_cat$PoolQC[is.na(housedata_cat$PoolQC)]<-"NoPool"
table(housedata_cat$PoolQC)


levels(housedata_cat$Fence)<-c(levels(housedata_cat$Fence),"NoFence")
housedata_cat$Fence[is.na(housedata_cat$Fence)]<-"NoFence"
table(housedata_cat$Fence)

levels(housedata_cat$MiscFeature)<-c(levels(housedata_cat$MiscFeature),"NoMiscFeature")
housedata_cat$MiscFeature[is.na(housedata_cat$MiscFeature)]<-"NoMiscFeature"
table(housedata_cat$MiscFeature)

levels(housedata_cat$FireplaceQu)<-c(levels(housedata_cat$FireplaceQu),"None")
housedata_cat$FireplaceQu[is.na(housedata_cat$FireplaceQu)]<-"None"
table(housedata_cat$FireplaceQu)


```






```{r}
housedatac<-housedata
housedatac$MSSubClass<-as.factor(housedata$MSSubClass)
str(housedatac)



```{r}
housedatac<-housedata
housdatac<-housedatac[,c("Id")]
#house_NA_I<-housedatac[,-c('Alley','FireplaceQu','PoolQC','Fence'	,'MiscFeature')]
#house_NA_R<-housedatac[,-c(1,2,3)]
#housedatac<-housedatac[,-c(7,58,73,74,75)]


```



Correlation between numerical variables
```{r}
library(corrplot)
corrplot(cor(housedata_num,use="complete.obs"), method="ellipse")
cor(housedata_num,use="complete.obs")
```
Correlation between numerical variables
```{r}

corrplot(cor(housedata_num), method="number")
```
# Side work - checking relationship between lot area and lot frontage
```{r}
plot(housedata_num$LotFrontage,housedata_num$LotArea, xlim=c(0,200),ylim=c(0,60000))
lm(housedata_num$LotFrontage~housedata_num$LotArea)

```
Feature selection

```{r}
library(MASS)


housedata_clean<-data.frame(c(housedata_cat,housedata_num))

housedata_clean2<-na.omit(housedata_clean)
full1<-lm(housedata_num$SalePrice~housedata_num$MSSubClass,data=housedata_num)
#full<-lm(housedata_clean2$SalePrice~., data=housedata_clean2)
#null<-lm(housedata_clean$SalePrice~1, data=housedata_clean)
#StepF<-StepAIC(null, scope=list(lower=null, upper=full), direction="foward", trace=TRUE)
str(housedata_clean2)
```

Plot the numerical variables
```{r}
#install.packages("VIM")
#library(VIM)
#summary(housedatac)
#housedata_imp<-kNN(housedata_cat,variable="LotFrontage", k=6)
```