---
title: "Step 4.2 Quantile Regression"
author: "Hyunkyung Kim"
date: "November 6, 2018"
output: pdf_document
---

I had so many errors trying to use quantile regression tool, so my used variables are quite limited and this is very basic.

```{r}
#install.packages("glmnet")
#install.packages("mlbench")
#install.packages("Boruta")
library(caret)
library(tidyverse)
library(psych)
library(glmnet)
library(mlbench)
library(Boruta)
library(MASS) # stepwise regression
library(leaps) # all subsets regression
library(randomForest)
library(MLmetrics)
library(quantreg)

```

```{r}
set.seed(999)
Mycontrols<-trainControl(method='repeatedcv',number=10, repeats=5,verboseIter = F)
```
### Import Cleaned Data

```{r}

H_Clean<-read.csv( file = "C:\\Users\\Hyunkyung Kim\\Desktop\\CKME999\\136\\dataset\\all\\H_clean.csv")

Train<-H_Clean[!is.na(H_Clean$SalePrice),-1] #Remove ID
Test<-H_Clean[is.na(H_Clean$SalePrice),-1] 
```

```{r}

Y<-Train[,80]
Ylog<-log10(Y)
X1<-Train[,unlist(lapply(Train, is.numeric))]
b<-apply(X1,2,sd)
b[b>2]
#X1<-Train[,unlist(lapply(Train, is.numeric))]
X2<-cbind(Train$LotArea,Train$YearBuilt,Train$GrLivArea,Train$TotalBsmtSF, Train$GarageArea ,Train$OverallCond+Train$YearBuilt+Train$OVerallcond + Train$OverallQual)
colnames(Train)

MyQR<-rq(Y~X2, tau= seq(0.05,0.95,by=0.05), data=Train)
MyQRLog<-rq(Ylog~X2, tau= seq(0.05,0.95,by=0.05), data=Train)
```
```{r}
plot(summary(MyQR))
plot(summary(MyQRLog))
summary(MyQRLog)
```

For regular prediction 
the coefficients do not vary too much from mean (red lines) for LotArea,
However, the effect decreases for the YearBuilt.
GrLivArea seems to be a bigger factor for the higher quantile.
TotalBsmtSF, Tr
GarageArea ,Train$\\OverallCond+Train$YearBuilt+Train$OVerallcond + Train$OverallQua